\documentclass[12pt, a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8x]{inputenc}
\usepackage{indentfirst} %indentace prvního odstavce
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{float}
\usepackage[czech]{babel}
\usepackage{mathdots}
\usepackage{slashbox}

\newcommand{\qed}{\hfill\square}

\begin{document}
\begin{center}
\large NMMB538 - Zkouška

\normalsize Jan Oupický
\end{center}
\vspace{1\baselineskip}

\textbf{Lemma Q.1.} \textit{Proof:}

Denote $h = x_2^2 - f(x_1)$ and assume $h = u \cdot v$ where $u, v \in \bar{K}[x_1,x_2]$. 

First assume $u,v \in \bar{K}[x_1,x_2] \setminus \bar{K}[x_1]$ i.e. $\deg_{x_2}(u) > 0, \deg_{x_2}(v) > 0$. Because $\deg_{x_2}(u) + \deg_{x_2}(v) = \deg_{x_2}(h) = 2 \implies \deg_{x_2}(u) = 1 = \deg_{x_2}(v)$. W.l.o.g assume $lc_{x_2}(u)=1=lc_{x_2}(v)$, we can do that since $lc_{x_2}(h)=1$. Therefore we can write $u = x_2 - s_1$ and $v = x_2 - s_2$ where $s_1, s_2 \in \bar{K}[x_1]$. This gives us
\[
x_2^2 - f(x_1) =h = (x_2 - s_1)(x_2 - s_2) = x_2^2 - (s_1+s_2)x_2 + s_1 s_2
\]
So it must hold that $s_1 = -s_2$ and then $h = x_2^2 + s_1(-s_1) \implies f(x_1) = s_1^2$. 

Now assume w.l.o.g $u \in \bar{K}[x_1]$.We compare the leading coefficients.
\[
1 = lc_{x_2}(h) = lc_{x_2}(u) \cdot lc_{x_2}(v) = u \cdot lc_{x_2}(v)
\]
This shows that $u$ must be invertible in $\bar{K}[x_1,x_2] \implies u \in \bar{K}^*$. In other words $h$ is absolutely irreducible. 

$\qed$

\textbf{Sublemma Q.3.5} \textit{Let $F/K$ be an algebraic function field, $char(K) \neq 2$, that is given by $y^2 = f(x)$, $f$ being a quaternary polynomial that posseses a simple root. Let $P \in \mathbb{P}_{F/K}$. If $x \notin P$ or $y \notin P$, then $x,y \notin P$ and $2v_P(x)=v_P(y)$}.

\textit{Proof:}
In $F$ it holds $y^2 = f(x)$ by definition which implies that for every $P \in \mathbb{P}_{F/K}$ $v_P(y^2) = 2v_P(y)=v_P(f(x))$.

Assume $v_P(x) < 0 \leq v_P(y)$. By properties of valution we have $\deg(f)v_P(x) = v_P(f(x)) = 2v_P(y) \implies 2v_P(x)=v_P(y)$ and by assumption $v_P(y) > v_P(x) \implies 2v_P(x) > v_P(x) \iff v_P(x) > 0$. That's a contradiction.

Now assume $v_P(x) \geq 0 > v_P(y)$. $v_P(x) \geq 0 \implies v_P(f(x)) \geq 0$ then $0 \leq v_P(f(x)) = 2v_P(y) < 0$ which is again a contradiction.

We have proven $v_P(x) < 0 \iff v_P(y) < 0$. Therefore we have the equality $4v_P(x) = 2v_P(y) \iff 2v_P(x) = v_P(y)$ assuming $v_P(x) < 0$ or $v_P(y) < 0$. 

$\qed$

\textbf{Lemma Q.4.} \textit{Proof:}
By sublemma Q.3.5 we know, that if $P \in \mathbb{P}_{F/K}: x^{-1} \in P \implies y^{-1} \in P$ and $2v_P(x)=v_P(y)$. This proves $(y)_{-}=2(x)_{-}$ ($x^{-1},y^{-1}$ "share" places and the valuation is 2:1).

Let's first assume that $f$ possesses a multiple root. Therefore $f(x_1) = (x_1-\alpha)^2g(x_1)$ where $\deg(g) = 2$ and $g$ is not a square. By Q.3 $F$ is given by $z^2 = g(x)$ i.e. $F=K(x,z)$. $[F:K(x)]=2$ since $min_{z,K(x)}(T) = T^2 - g(x)$, that polynomial has $z$ as a root in $F$ and it is absolutely irreducible (as a polynomial in $K[x,T]$) since $g$ is not a square. We can then assume $\bar{K}=K$ since $[F:\bar{K}(x)] = 2$ (same polynomial) and $[F:K(x)] = [F:\bar{K}(x)][\bar{K}:K] = 2 \implies [\bar{K}:K] = 1$.

Then we know $\deg((x)_{-}) = [F:K(x^{-1})] = [F:K(x)] = 2$ i.e. $\deg(D)=2$.

Now assume $f$ is separable. We can then use the same argument for $K=\bar{K}$ since $min_{y,K(x)}(T) = T^2-f(x)$ and by Q.1 this one is also absolutely irreducible. $F=K(x,y) \implies [F:K(x)] = [F:\bar{K}(x)][\bar{K}:K] = 2 \implies [\bar{K}:K]=1$. And again $\deg(D)=2$.

Now let's prove that the genus is at most 1. Since $\deg(D)=2 \implies \sum\limits_{P: x^{-1}\in P} v_P(x)\deg(P) = 2$ means we have 2 possibilities (we are assuming $K=\bar{K}$ which implies $\forall P \in \mathbb{P}_{F/K}: \deg(P)=1$:
\begin{enumerate}
    \item There exists a unique place $P_\infty: v_{P_\infty}(x)=-2, v_{P_\infty}(y)=-4$ and $D = 2P_\infty$
    \item There are 2 distinct places $P,Q$ s.t. $v_P(x)=-1=v_Q(x), v_P(y)=-2=v_Q(y)$ and $D = P + Q$.
\end{enumerate}

In both cases we can see that for $k \geq 2: \{1,x,\dots,x^k, y, yx, \dots, yx^{k-2}\} \subset \mathcal{L}(kD)$ because $(x^k) + kD = k((x)_{+}-(x)_{-})+k(x)_{-} = k(x)_{+} \geq 0$ and also $(y)_{-}=2(x)_{-}$ so it holds if we substitute $x^2$ for $y$. This subset is linearly indepent over $K$ because $y$ cannot be expressed as a linear combination of $x^i$ since $f$ has one simple root (if $f(x)=g^2(x) \implies y=g(x)$). The set also contains $2k$ elements. Therefore $l(kD) \geq 2k$. 

We know that for a sufficiently large $k$ (if $l(kD) \geq 2g-1$, $g$ genus) we have $l(kD) = \deg(kD)-g+1$ having $\deg(kD)=2k, l(kD) \geq 2k \implies 0 \leq l(kD)-\deg(kD) = -g + 1 \iff g \leq 1$.

$\qed$

\textbf{Proposition Q.5.} \textit{Proof:}
As noted by paragraph before Q.5. w.l.o.g. we can assume $f(x) = x^4+bx^2+cx+d$. Denote $bx^2+cx+d = g(x)=f(x)-x^4$. First we will prove that for both $z \in Z = \{y+x^2, y-x^2\}: [F:K(z)]=2$. 

Denote $z_1=y+x^2, z_2=y-x^2$. First we show that $F=K(x,z_i)$ for $i=1,2$. $F$ can be expressed as $K(x,y)$. $y\in K(x,z_i)$ since $z_i \pm x^2 = y$. This shows $F \subseteq K(x,z_i)$ and the converse is obvious. Also $K(x,z_i) \neq K(z_i)$ because for genus 1 it is a contradiction. If genus is 0 then $F=K(x+y)$ and it would mean $K(x+y)=K(y \pm x^2)$. 

We will find minimal polynomial $m(T)$ of $x$ over $K(z_1)$ then $\deg(m) = [F:K(z_1)]=[K(x,z_1):K(z_1)]$. $z_2 = z_1 - 2x^2$ and $z_1z_2=y^2-x^4=g(x)$. Then:
\begin{gather*}
z_1(z_1-2x^2) = g(x) = bx^2+cx+d
\end{gather*}
Then $m(T)=z_1(z_1-2T^2)-bT^2-cT-d \in K(z_1)[T]$. $\deg(m)=2$ and $m(x)=0$ and $F\neq K(z_1) \implies$ this must be a minimal polymial of $x$ over $K(z_1)$.

In a similar way we can find a minimal polynomial of $x$ over $K(z_2): m(T) = z_2(z_2+2T^2)-bT^2-cT-d \in K(z_2)[T]$.

We have shown $[F:K(z_i)]=2$.


Choose $P \leq D$ a place. We will prove that for at least one $z \in Z: v_P(z) < v_P(x)$.
\begin{gather*}
y^2 = f(x) \iff y^2 - x^4 = g(x), 0 \leq \deg(g) \leq 3 \implies\\
(y+x^2)(y-x^2)=g(x) \implies v_P(y+x^2)+v_P(y-x^2) = v_P(g(x)) = \deg(g)v_P(x)
\end{gather*}
Denote $z_1 = y+x^2, z_2=y-x^2$. Assume to contrary $v_P(z_1) \geq v_P(x)$ and $v_P(z_2) \geq v_P(x)$. We will look at all possible cases.

$\deg(g)=3$: $3v_P(x)=v_P(z_1)+v_P(z_2) \geq v_P(x)+v_P(x) \implies v_P(x) > 0$ which is a contradiction since $v_P(x)<0$.

$\deg(g)=2$: $2v_P(x)=v_P(z_1)+v_P(z_2)$. 

First consider $v_P(x)=v_P(z_1)=v_P(z_2)$ and $v_P(x)=-2$, then $2P = (x)_{-}= (z_1)_{-} = (z_2)_{-}$. Then $z_1, z_2 \in \mathcal{L}(D)$ but then also $\frac{z_1+z_2}{2} = y \in \mathcal{L}(D)$ which is a contradiction since $(y)_{-}=2(x)_{-}$.

Now let's assume $v_P(x)=-1$ and then there also exist a different place $Q$ s.t. $v_Q(x)=v_Q(z_1)=v_Q(z_2)=-1$. Since $\deg((z)_{-})=2$ then again $P+Q = (x)_{-}= (z_1)_{-} = (z_2)_{-}$ and we have the same contradiction.

We have proven that $v_P(x)=v_P(z_1)=v_P(z_2)$ is impossible therefore for one $z$ it must hold $v_P(z)<v_P(x)$.

$\deg(g)=1$: $v_P(x)=v_P(z_1)+v_P(z_2)$. First assume $v_P(x)=-2$. And also $v_P(z_1)=v_P(z_2)=-1$. This is impossible since $\deg((z)_{-})=2$ but for every other place $Q \neq P: 0 = v_Q(z_1)+v_Q(z_2) \implies v_Q(z_1)=-v_Q(z_2)$. If there was $Q_1: v_{Q_1}(z_1)=-1 \implies v_{Q_1}(z_2)=1$ and $Q_2: v_{Q_2}(z_2)=-1 \implies v_{Q_2}(z_1)=1$. Then for some $P_1,P_2$ places of degree 1: $(z_1)=(P_1+Q_2)-(P+Q_1), (z_2)=(P_2+Q_1)-(P+Q_2)$. Set $D'=P+Q_1+Q_2$ then $z_1,z_2 \in \mathcal{L}(D')$ and as before this means that $y \in \mathcal{L}(D')$ which is a contradiction.

Now if $v_P(x)=-1$ then either $v_P(z) < v_P(x)$ for a $z \in Z$ or w.l.o.g $v_P(z_1)=-1$ and $v_P(z_2)=0$. Then also assume first $v_Q(z_1)=-1 \implies v_Q(z_2)=0$. But since $\deg((z)_{+})=2$ there must be a place $P'$ s.t. $v_{P'}(z_2)>0$ and $v_{P'}(x)=0$ since $P'\neq P,Q$ but it must be $v_{P'}(z_1) < 0$. This again contradicts the degree of the divisor. 

If $v_Q(z_1)=0$ and $v_Q(z_2)=-1$. Then again there must be a place $P_1$ s.t. $v_{P_1}(z_1)=-1$ and $v_{P_1}(z_2)=1$ and a place $v_{P_2}(z_2)=1 \implies v_{P_2}(z_1)=-1$. This also contradicts divisor degree.

The last case is $\deg(g)=0$: $v_P(z_1)=-v_P(z_2) \implies (z_1) = -(z_2)$. First assume $v_P(z_1)=0 \implies v_P(z_2)=0$ and same for $v_Q$ ($Q$ not necessarly different from $P$). Then there exist places $P_1,P_2,Q_1,Q_2 \neq P,Q$ s.t. $(z_1)=P_1+P_2-(Q_1+Q_2), (z_2)=-(z_1)$. Set $D' = P_1+P_2+Q_1+Q_2$ then $z_1,z_2 \in \mathcal{L}(D')$ but also $y \in \mathcal{L}(D')$ which is again contradiction since $(y)_{-}=2(x)_{-}$.

If $v_P(z_1)=1 \implies v_P(z_2)=-1$. There exists another place $P'$ s.t. $v_{P'}(z_1)=1 \implies v_{P'}(z_2)=-1$. There must be again two places $Q_1,Q_2$ s.t. $(z_1)=P+P'-(Q_1+Q_2), (z_2) = -(z_1)$. Put $D' = P+P'+Q_1+Q_2$ then again $y \in \mathcal{L}(D')$ which is a contradiction.
\\

We have proven that for each place $P \leq D$ at least one $z \in Z$ must have $v_P(z)<v_P(x)$. This shows also that $(x)_{-}=P+Q$ for distinct $P,Q$. If $P=Q$ then $v_P(x)=-2 \implies v_P(z)\leq -3$ which contradicts $[F:K(z)]=2$. Since $\deg((z)_{-})=2$ and $v_P(z) < -1$ it must be that $(z)_{-}=2P, (z')_{-}=2Q$ for $z,z' \in Z$. Since we have not distinguished $P$ and $Q$ we can say $(z_1)_{-}=2P$ and $(z_2)_{-}=2Q$.



$\qed$


\textbf{Theorem Q.6.} \textit{Proof:}
Assume genus 0. There exists $t \in F$ s.t. $(t)=P-Q$ and also $(t^{-1})=-(t)=Q-P$. Also $l(D)=\deg(D)+1 = 3$. 

$t \in \mathcal{L}(D)$ since $(t)+D = P-Q+P+Q=2P \geq 0$. Also $t^{-1} \in \mathcal{L}(D): (t^{-1})+D=Q-P+P+Q = 2Q \geq 0$. $t$ and $t^{-1}$ are linearly independent since $t \notin K$. This means $\{1,t,t^{-1}\}$ is a basis of $\mathcal{L}(D)$.

$x \in \mathcal{L}(D) \implies x = c_0+c_1t+c_2t^{-1}$ for some $c_i \in K$. This is equivalent to saying $tx = u(t), u(t) \in K[t], \deg(u)=2$.

In the same way we see $\{1,t,t^{-1},t^2,t^{-2}\}$ for a basis of $\mathcal{L}(2D)$. Again $y \in \mathcal{L}(2D): (y) + 2D = (y)_{+} - (y)_{-} + 2(x)_{-} = (y)_{+} \geq 0$. This means $t^2y = v(t)$ where $v(t) \in K[t], \deg(v)=4$.

$y^2 = f(x) \iff t^4y^2=t^4f(x)$. Substitute $yt=v(t)$ and $xt^2=u(t)$ then we have equality $v^2(t)=t^4f(\frac{u(t)}{t})$. $f$ is a polynomial of degree $4$ therefore it has up to $4$ different roots $1 \leq i \leq 4: \alpha_i \implies v^2(t)=t^4(\frac{u(t)}{t}-\alpha_1)(\frac{u(t)}{t}-\alpha_2)(\frac{u(t)}{t}-\alpha_3)(\frac{u(t)}{t}-\alpha_4)$ we can rewrite this as 
\begin{gather*}
v^2(t)=(u(t)-t\alpha_1)(u(t)-t\alpha_2)(u(t)-t\alpha_3)(u(t)-t\alpha_4)
\end{gather*}
$v^2(t)=v(t)v(t)$ is a polynomial of degree $8$, which has at most 4 different roots. Also $u(t)-t\alpha_i$ is a polynomial of degree 2. There exist at most two $\alpha \in K$ s.t. $u(t)-t\alpha$ has a root of multiplicity 2. This is because the root of a quadratic polynomial has multiplicity 2 when the discriminant D is 0. If $g(x)-\alpha x=ax^2+(b-\alpha)x+c \implies 0 = \text{D} = (b-\alpha)^2-4ac \iff \alpha = \pm 2\sqrt{ac}+b$.

Also if $i\neq j: \alpha_i \neq \alpha_j$ the polynomials $u(t)-t\alpha_i$ and $u(t)-t\alpha_j$ do not have common roots. This means that if $1 \leq i \leq 4: \alpha_i$ are all different then $v^2(t)$ has at least $6 = 2+2+1+1$ different roots. This a contradiction.

Therefore if genus is $0$ then $f$ cannot be separable. We have shown that genus of $F$ is 0 or 1, this means that for $f$ separable we must have genus 1.

Denote $w=x_2^2-f(x_1)$.
\begin{gather}
\frac{\partial w}{\partial x_1} = -f'(x_1), \frac{\partial w}{\partial x_1} = 2x_2
\end{gather}
For a singularity $\alpha = (\alpha_1, \alpha_2), \alpha_2$ must be $0$ and $\alpha_1$ must be a root of $f(x_1)$ and also of $f'(x_1)$ this is true iff $f(x_1)$ is separable. If $f(x_1)$ is not separable then it shares a common root $\alpha_1$ with $f'(x_1)$ and this gives us singularity at $(\alpha_1, 0)$. This proves the rest of the theorem.

$\qed$

\textbf{Theorem Q.7.} \textit{Proof:}
Denote $D = P + Q$ a divisor. Due to genus being 1 $\forall k\geq 1: l(kD) = 2k$. $l(D)=2$ and that means there exists $x \notin K$ s.t. $\{1,x\}$ is a basis of $\mathcal{L}(D)$ and also $(x)_{-} \leq P+Q$. Then $(x)^2 = 2(x) = 2(x)_{+}-2(x)_{-} \implies x^2 \in \mathcal{L}(2D),\{1,x,x^2\}$ is linearly independent in $\mathcal{L}(2D)$ but $l(2D)=4$ that means there exists $y \in \mathcal{L}(2D)\setminus \mathcal{L}(D)$ such that $\{1,x,x^2,y\}$ is a basis of $\mathcal{L}(2D)$. 

Denote $B = \{1,x,x^2,x^3,x^4,y,yx,yx^2,y^2\}$, clearly $B \subseteq \mathcal{L}(4D), l(4D)=8$ and $|B|=9 \implies 1 \leq i \leq 8: \exists a_i \in K:$
\begin{gather*}
y^2 = a_1y + a_2yx + a_3yx^2 + a_4x^4 + a_5x^3 + a_6x^2 + a_7x+ a_8
\end{gather*}

Denote $C = \{1,x,x^2,x^3,y,yx\}$. $C$ is a basis of $\mathcal{L}(3D)$, $C \cup \{yx^2,y^2\}$ is also a basis of $\mathcal{L}(4D)$. If $a_4=0$ that would be a contradiction to $C \cup \{yx^2,y^2\}$ being a basis of $\mathcal{L}(4D)$ since $y^2$ would be a linear combination of 7 elements.

Now we make a substitution $y \rightarrow y - \frac{a_1+a_2x+a_3x^2}{2}$. This gives us form:
\begin{gather*}
y^2 =b_1x^4 + b_2x^3 + b_3x^2 + b_4x+ b_5
\end{gather*}
where $b_1 = a_4+\frac{a_3^2}{4}$. If $b_1=0$ then $y^2$ would be a linear combination of elements in $\mathcal{L}(3D)$ but 

$\qed$

\textbf{Theorem Q.8.} \textit{Proof:}
Denote $f(x) = g(x^2)$. $F$ is EFF therefore genus is 1 and there exists a place of degree $1$. Also $K$ can be assumed algebraically closed.

If $g(x)$ has a multiple root $\alpha$, then $f(x)=g(x^2)$ has also a multiple root because $g(x)=(x-\alpha)^2 \implies g(x^2) = (x-\sqrt{\alpha})^2(x+\sqrt{\alpha})^2$. Set $z = \frac{y}{x-\sqrt{\alpha}}$. Then $F$ is given by $z^2=(x+\sqrt{\alpha})^2$. This means $x \in K(z)$ and from the definition of $y$ also $y \in K(z)$ which means $F$ has genus 0, a contradiction.

From now on we can assume $g(x)$ has 2 distinct roots. If $f(x)=g(x^2)$ would have a multiple root then it's genus would not be $1$ by Q.6. So we can assume $g(x^2)$ separable. 

First we will prove the second part of the theorem. We have shown that $g(x^2)$ must be separable. Therefore by Q.5 we have places of degree 1 ($P\neq Q$), $(x)_{-} = P+Q$ and $(y+x^2)_{-}=2Q, (y-x^2)_{-} = 2P$.
\begin{gather*}
y^2=g(x^2) = x^4+2bx^2+c \iff y^2-(x^4-2bx^2-b^2) = c - b^2 \implies \\
(y-(x^2+b))(y+(x^2+b))=c-b^2
\end{gather*}

Since $g(x^2)$ is separable $g(x)$ must have simple roots. If $g(x)$ has a multiple root then it's discriminant is 0 and that happens iff $c-b^2=0$. So we know $0 \neq c-b^2 \in K$.

\begin{gather*}
0=v_P(c-b^2)=v_P(y-(x^2+b)) + v_P(y+(x^2+b))\\
v_P(y-(x^2+b)) = v_P(y-x^2) = -2 \implies v_P(y+(x^2+b)) = 2
\end{gather*}

Similarly we can show $v_Q(y-(x^2+b)) = 2$ and $v_Q(y+x^2+b)=-2$. 

Since $\deg((y+x^2+b)_{+}) = \deg((y+x^2+b)_{-}) = \deg((y+x^2)_{-}) = 2 \implies \text{div}(y+x^2+b) = 2P - 2Q$ and similarly $\text{div}(y+x^2+b) = 2Q - 2P$.

We have proven the last part of the theorem. Now let's prove the equivalence.

As we have shown before. We can assume $g(x^2)$ separable and then we have involution $P-Q$ as shown above since $2P-2Q = (t)$ for $t \in F$. We only have to show that $P-Q \neq (t)$ for some $t \in F$. 

If $t \in F$ s.t. $(t) = P - Q \implies \deg((t)_{+}) = 1 = [F:K(t)]$ and that would be contradiction with F being EFF.

Now we assume we have involution. We can always find $t \in F \setminus K$ s.t. $(t) = 2P-2Q$ where $P,Q$ distinct places of degree 1 and $P-Q$ is involution.

Then $l(2P) = 2 = l(2Q) \implies \{1,t\}$ is a basis of $\mathcal{L}(2P)$ and $\{1,t^{-1}\}$ is a basis of $\mathcal{L}(2Q)$.

$\qed$


\textbf{Proposition G.2} \textit{Proof:}
Since $F/K$ is given by $y^2 = g(x^2)$ we know that $F=K(x,y)$.

Clearly $K(\tilde{x},\tilde{y}) \subseteq K(x,y)$. The other inclusion is also clear since $x = \tilde{x}^{-1}\tilde{y}$ and $y = 2\tilde{x}-x^2-b$. 

Now we need to show that $-\tilde{y}^2+\tilde{x}^3-b\tilde{x}^2+\frac{b^2-c}{4}\tilde{x} = 0$ in $F$.

\begin{gather*}
\tilde{y}^2 = \tilde{x}^3-b\tilde{x}^2+\frac{b^2-c}{4}\tilde{x}\\
\text{Substitute $\tilde{x}, \tilde{y}$:}\\
\frac{x^2u^2}{4} = \frac{u^3}{8} - \frac{bu^2}{4} + \frac{b^2-c}{8}u\\
2x^2u^2 = u^3 - 2bu^2 + (b^2-c)u \\
\text{Divide by $u \neq 0$ in $F$:}\\
2x^2u = u^2 - 2bu + (b^2-c)\\
\text{Substitute $u=y+x^2+b$:}\\
2x^2(y+x^2+b) = (y^2+x^4+2yx^2+2by+2bx^2+b^2)-2b(y+x^2+b)+b^2-c\\
\iff\\
y^2-x^4-2bx^2-c = y^2 - g(x^2)= 0
\end{gather*}
We have shown that $\tilde{y}^2 = \tilde{x}^3-b\tilde{x}^2+\frac{b^2-c}{4}\tilde{x}$ in $F$ since $y^2=g(x^2)$ in $F$ by definition.

The only thing left is to show that $y^2-x^3+bx^2+\frac{b^2-c}{4}x$ is irreducibile in $K[x,y]$. Using Einsenstein criterion with $x \in K[x]$ as a prime element we get that this polynomial is indeed irreducibile in $(K[x])[y]$.

$\qed$

\textbf{Theorem G.3} \textit{Proof:}
Assume we have $(a_2, a_4) \in K \times K$ s.t. $a_4 \neq 0 \neq a_2^2-4a_4$. Set $b = -a_2$ and $c = -4a_4+a_2^2$. If $c = 0$ this would mean that $4a_4=a_2^2$ which is a contradiction with $a_2^2-4a_4 \neq 0$. If $b^2-c=0 \iff c=b^2$ then this is would imply $-4a_4+a_2^2 = a_2^2 \iff a_4 = 0$ which is again a contradiction.

On the other hand assume we have $(b,c) \in K \times K$ s.t. $c \neq 0 \neq b^2-c$. Set $a_2 = -b, a_4 = \frac{b^2-c}{4}$. If $a_4 = 0$ this would imply $b^2-c = 0$ which is contradiction. If $a_2^2-4a_4 =0 \iff b^2=b^2-c \iff c = 0$ which is a contradiction.

We have therefore proven that $G.1$ holds.

Denote the rational map $C_1 \rightarrow C_2$ as $\psi$ and the map $C_2 \rightarrow C_1$ as $\phi$. Also $f(x_1,x_2) = x_2^2-x_1^3-a_2x_1^2-a_4x_1, C_1 = V_{f}, g(x_1,x_2) = x_2^2-x_1^4-2bx_1^2-c, C_2 = V_g$.

Now we need to show that $\psi$ and $\phi$ are actually $K$-rational maps. We will use lemma $R.6$ from the lecture. 

First we know that $\phi$ is a rational map thanks to proposition $G.2$. By proposition $G.2$ (since $a_2 = -b, a_4 = \frac{b^2-c}{4}$) we have shown that $(\rho_1,\rho_2) = 0 \in K(C_2)$ where $(\rho_1,\rho_2) = \left(\frac{x_2+x_1^2+b}{2} + (g), \frac{x_1(x_2+x_1^2+b)}{2} + (g)\right)$. By lemma $R.6$ this means that $\phi$ is a $K$-rational map $C_2 \rightarrow C_1$.

To show that $\psi$ is a $K$-rational map $C_1 \rightarrow C_2$ we need to prove that $g(\rho_1, \rho_2) = 0 \in K(C_1)$ where $(\rho_1, \rho_2) = \left( \frac{x_2}{x_1} + (f), \frac{x_1^2-a_4}{x_1} + (f)\right)$.

\begin{gather*}
g(\rho_1, \rho_2) = \frac{(x_1^2-a_4)^2}{x_1^2} - \frac{x_2^4}{x_1^4} - 2b\frac{x_2^2}{x_1^2} - c\\
g(\rho_1, \rho_2) = 0 \iff x_1^4g(\rho_1, \rho_2) = 0 \text{ and using $b=-a_2, c = a_2^2-4a_4$}\implies\\
x_1^4g(\rho_1, \rho_2) = -x_2^4 + 2a_2x_1^2x_2^2+x_1^6+2a_4x_1^4-a_2^2x_1^4+a_4^2x_1^2\\
\text{Substitution $x_1^6 = (x_2^2-a_2x_1^2-a_4x_1)^2$:}
x_1^4g(\rho_1, \rho_2) = -2a_4x_1x_2^2+2a_4x_1^4+2a_2a_4x_1^3+2a_4^2x_1^2 = \\
2a_4x_1(-x_2^2+x_1^3+a_2x_1^2+a_4x_1) = 0 \in K(C_1)
\end{gather*}
This proves that $\psi$ is a $K$-rational map $C_1 \rightarrow C_2$.


By definition of birational equivalence we need to show that $\phi \circ \psi = id_{C_1}$ and $\psi \circ \phi = id_{C_2}$.

Let's start with $id_{C_1}$, we want to show that $\phi \circ \psi$ can be represented as $(x_1, x_2) \in K(C_1)$. First coordinate:
\begin{gather*}
\frac{\frac{x_1^2-a_4}{x_1}+\frac{x_2^2}{x_1^2}+b}{2} = \frac{x_1^3-a_4x_1+x_2^2+x_1^2b}{2x_1^2}\\
\text{Substitution for $x_2^2$ in $K(C_1)$ and using $b=-a_2$:}\\
\frac{2x_1^3}{2x_1^2} = x_1
\end{gather*}
Second coordinate (again using $b=-a_2$):
\begin{gather*}
\frac{\frac{x_2}{x_1}\left(\frac{x_1^2-a_4}{x_1} + \frac{x_2^2}{x_1^2} - a_2 \right)}{2} = \frac{x_2(x_1^3-a_4x_1+x_2^2-a_2x_1^2)}{2x_1^3}\\
\text{Substitution for $x_2^2$ again:}\\
\frac{x_2(2x_1^3)}{2x_1^3} = x_2
\end{gather*}
We have shown that $\phi \circ \psi = id_{C_1}$ i.e. 

Now for $\psi \circ \phi$. First coordinate:
\begin{gather*}
\frac{\frac{x_1(x_2+x_1^2+b)}{2}}{\frac{x_2+x_1^2+b}{2}} = \frac{x_1(x_2+x_1^2+b)}{x_2+x_1^2+b} = x_1
\end{gather*}
Second coordinate:
\begin{gather*}
\frac{\left(\frac{x_2+x_1^2+b}{2}\right)^2 - a_4}{\frac{x_2+x_1^2+b}{2}} = \frac{\frac{x_2^2+x_1^4+2x_1^2x_2+2bx_2+2bx_1^2+b^2-4a_4}{4}}{\frac{x_2+x_1^2+b}{2}}\\
\text{Using substitution for $x_1^4$ in $K(C_2)$ and $-4a_4 = -b^2+c$:}\\
\frac{2x_2^2+2x_1^2x_2+2bx_2}{2x_2+2x_1^2+2b} = x_2
\end{gather*}
We have proved that both compositions of those rational maps are identitities therefore $C_1$ and $C_2$ are birationally equivalent.

$\qed$

\textbf{Theorem G.4} \textit{Proof:}
Assume we have $(a_2, \gamma) \in K \times K$ s.t. $\gamma^2 \neq 0 \neq a_2^2-4\gamma^2$. Set $B = \gamma^{-1}, A = a_2\gamma^{-1}$. Since $\gamma \neq 0$ then also $\gamma^{-1} = B$ cannot be 
0. If $A^2 = 4$ then $a_2^2\gamma^{-2} = 4 \iff a^2 - 4\gamma \neq 0$ which is a contradiction.

On the other hand if we have $(A,B) \in K \times K$ s.t. $B(A^2-4)\neq 0$ then set $\gamma = B^{-1}$ and $a_2 = AB^{-1}$. If $\gamma^2 = 0$ this would imply $\gamma = 0$ which is a contradiction with $B \neq 0$. If $a_2^2-4\gamma^2 =0 \iff a_2^2 = 4\gamma^2$ this would imply $\frac{A^2}{B^2} = 4B^{-2} \iff A^2 = 4$ which is again contradiction.

We have therefore proven that $G.2$ holds.

As in $G.3$ denote $f(x_1,x_2) = x_2^2-x_1^3-a_2x_1^2-a_4x_1, C_1 = V_f$ and $g(x_1,x_2) = Bx_2^2-x_1^3-Ax_1^2-x_1, C_2 = V_g$. Denote the rational map $C_1 \rightarrow C_2$ as $\psi$ and the rational map $C_2 \rightarrow C_1$ as $\phi$.

First we show that $\psi$ is a $K$-rational map $C_1 \rightarrow C_2$ using $R.6$ as in $G.3$. We want to show $g(\rho_1, \rho_2) = 0 \in K(C_1)$ where $(\rho_1, \rho_2) = \left(\gamma^{-1}x_1 + (f), \gamma^{-1}x_2 + (f) \right)$. We know that $\gamma^{-1} = \frac{1}{\sqrt{a_4}}$ and $a_4 \neq 0, B = \frac{1}{\sqrt{a_4}}, A = \frac{a_2}{\sqrt{a_4}}$.
\begin{gather*}
g(\rho_1, \rho_2) = \frac{1}{\sqrt{a_4}}\left( \frac{x_2}{\sqrt{a_4}} \right)^2 - \frac{x_1^3}{\sqrt{a_4}^3} - \frac{a_2}{\sqrt{a_4}}\frac{x_1^2}{\sqrt{a_4}^2} - \frac{x_1}{\sqrt{a_4}} = \frac{x_2^2-x_1^3-a_2x_1^2-a_4x_1}{a_4\sqrt{a_4}} = 0
\end{gather*} 

Now we want to show $f(\rho_1, \rho_2) = 0 \in K(C_2)$ where $(\rho_1, \rho_2) = \left( B^{-1}x_1 + (g), B^{-1}x_2+(g) \right)$. Similarly $a_4 = \frac{1}{B^2}$ since $B \neq 0$ and $a_2 = \frac{A}{B}$:
\begin{gather*}
f(\rho_1, \rho_2) = \frac{x_2^2}{B^2} - \frac{x_1^3}{B^3} - \frac{A}{B}\frac{x_1^2}{B^2}-\frac{1}{B^2}\frac{x_1}{B_1} = \frac{Bx_2^2-x_1^3-Ax_1^2-x_1}{B^3} = 0
\end{gather*}

So $\psi$ and $\phi$ are both $K$-rational maps. Now as in $G.3$ we show birational equivalence by proving $\phi \circ \psi = id_{C_1}$ and $\psi \circ \psi = id_{C_2}$ which is trivial in this case.
\begin{gather*}
\phi \circ \psi = (B^{-1}(Bx_1), B^{-1}(Bx_2)) = (x_1, x_2)\\
\psi \circ \phi = (\gamma^{-1}(\gamma x_1), \gamma^{-1}(\gamma x_2)) = (x_1, x_2)
\end{gather*}

$\qed$

\textbf{Proposition G.5} \textit{Proof:}
Assume we have $(a,d) \in K^* \times K^*, a \neq d$. Set $B =  \frac{4}{a-d}, A = \frac{2(a+d)}{a-d}$. $B \neq 0$ and if $A = 2$ then this is a contradiction with $d \neq 0$ and if $A = -2$ then it is contradiction with $a \neq 0$. 

On the other hand assume $(A,B) \in K \times K$ s.t. $B \neq 0$ and $A^2 \neq 4$. Set $a = \frac{A+2}{B}$ and $d = \frac{A-2}{B}$. If $a = 0$ or $d = 0$ this is a contradiction with $A \neq \pm 2 \iff A^2 \neq 4$. If $a=d \iff 2=-2$ which is a contradiction. We have shown that $G.3$ holds.

Denote the rational map $C_1 \rightarrow C_2$ as $\psi$ and the rational map $C_2 \rightarrow C_1$ as $\phi$. First let's prove that $\psi$ is a rational map.

Theorem $G.4$ gives us a $K$-rational map $\Psi_1: C_1 \rightarrow C'$ s.t. $\Psi_1(x_1, x_2) = (B^{-1}x_1, B^{-1}x_2)$ where $C' = V_f$ where $f(x_1, x_2) = x_2^2-x_1^3-a_2x_1^2-a_4x_1$ and $a_2 = \frac{A}{B}$ and $a_4 = \frac{1}{B^2}$. Theorem $G.3$ gives us a $K$-rational map $\Psi_2: C' \rightarrow C_2$ where $\Psi_2(x_1, x_2) = \left(\frac{x_2}{x_1}, \frac{x_1^2-a_4}{x_1} \right)$. We can use $G.3$ because due to the paragraph before $G.5$ we know that $C_2$ in $G.5$ and $C_2$ in $G.3$ are equal.

By composition of these 2 $K$-rational maps we get $\Psi_2 \circ \Psi_1 = \psi$. Since $\Psi_1, \Psi_2$ are $K$-rational maps of finite degree (because every $\rho$ we used in the proofs were transcendental over $K$) we get by Theorem $R.9$ from the lecture that $\psi$ is also a $K$-rational map $C_1 \rightarrow C_2$.

Using similar process theorem $G.3$ gives us a $K$-rational map $\Phi_1: C_2 \rightarrow C'$ s.t. $\Phi_1(x_1, x_2) = \left(\frac{x_2+x_1^2+b}{2}, \frac{x_1(x_2+x_1^2+b)}{2} \right)$ where $C' = V_g$ where $g(x_1,x_2) = x_2^2-x_1^3-a_2x_1^2-a_4x_1$ where $a_2 = -b, a_4 = \frac{b^2-c}{4}$ where (using paragraph above $G.5$) $b = \frac{-a-d}{2}, c = ad$ so in total $a_2 = \frac{a+d}{2}$ and $a_4 = \frac{(a-d)^2}{16}$. Theorem $G.4$ gives us a $K$-rational map $\Phi_2: C' \rightarrow C_1$ s.t. $\Phi_2(x_1, x_2) = (Bx_1, Bx_2)$ where in theorem $G.4$ we have $A = \frac{a_2}{\sqrt{a_4}}$ and $B = \frac{1}{\sqrt{a_4}}$. If we resubstitute we get $A = \frac{2(a+d)}{a-d}$ and $B = \frac{4}{a-d}$.

Again the composition $\Phi_2 \circ \Phi_1 = \phi$. Since $\Phi_2, \Phi_1$ are $K$-rational maps of finite degree then $\phi$ is a $K$-rational map $C_2 \rightarrow C_1$.

Now we need to show $\phi \circ \psi = id_{C_1}$ and $\psi \circ \phi = id_{C_2}$.
\begin{gather*}
\phi \circ \psi = (\Phi_2 \circ \Phi_1) \circ (\Psi_2 \circ \Psi_1) = \Phi_2 \circ (\Phi_1 \circ \Psi_2) \circ \Psi_1 = \Phi_2 \circ id_{C'} \circ \Psi_1 =\\
\Phi_2 \circ \Psi_1 = id_{C_1}
\end{gather*}
We have used Theorem $G.3$ which states $\Psi_2 \circ \Psi_1 = id_{C'}, \Phi_2 \circ \Psi_1 = id_{C_1}$. Similarly due to Theorem $G.5$:
\begin{gather*}
\psi \circ \phi = (\Psi_2 \circ \Psi_1) \circ (\Phi_2 \circ \Phi_1) = \Psi_2 \circ id_{C'} \circ \Phi_1 = \Psi_2 \circ \Phi_1 = id_{C_2}
\end{gather*}
We have shown that $C_1$ and $C_2$ are birationally equivalent.

$\qed$

\textbf{Lemma W.1} \textit{Proof:}


\end{document}